Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2019-07-07 unimodular-covers.tex
reviewed introduction + final changes to sec4

This not only implies \Cref{conj:Oda}(1) in dimension three, but also, as we show in \Cref{sec:cayley}, \Cref{conj:Oda}(2) for $3$-dimensional \emph{prismatoids}, polytopes whose vertices all lie in two parallel facets:

@@

\Paco{another corollary, suggested by Christian Haase: the $k$-th dilation of an emptyy simplex is very easy to decompose into slices of width one all of which fit into our description ($P$ and $Q$ are either pararllel parallelograms, one of which perhaps degenerates to a segment). In particular, we recover as a corollary that the $k$-th dilation of every empty tetrahedron (and, a fortiori, the $k$-th dilation of every lattice $3$-polytope) has a unimodular cover for every $k\ge 2$

EXCEPT FOR THIS TO BE TRUE WE NEED TO ALLOW $Q$ TO DEGENERATE TO AN EDGE IN \Cref{hm:cayley}. CAN WE?
}

We believe that the $3$-polytopes in these four statements all have unimodular triangulations, but we do not have a proof.

\subsection*{Acknowledgements:} We thank Akiyoshi Tsuchiya, Spencer Backman, Gaku Liu, Johannes Hofscheier, Christian Haase, .... et al.

%\section{Preliminaries}
%\label{Fprelim}

@@

Consider the segment $s$ contained in $r_1' + \vecline p$ with endpoints $s_1=r_1'$ on $d$ and $s_2$ on $d'$.

%By claim \ref{positive slopes}, $s_2$ lies above the affine line $\langle t \rangle$.

Since $t$ separates $q_1$ and $q_1+q_2-p_1$ and $g$ decreases from $t_1$ to $t_2$ (by \Cref{claim:g}), the inequality $g(x)< g(d')$ holds on $Q\cap V_2$,
and in particular for $r_2'$. Since $r_2'$ is a lattice point, $g(r_2')\leq g(d)= g(r_1')$, which contradicts \Cref{claim:g}).
\end{proof}
\giulia{add a picture!}

>>>>

This not only implies \Cref{conj:Oda}(1) in dimension three, but also the following two statements, that we prove in \Cref{sec:cayley}.
A $3$-dimensional \emph{prismatoids} is a polytopes whose vertices all lie in two parallel facets. A special case is a polytope of width $1$, whose vertices lie in two consecutive parallel lattice hyperplanes.

@@

\begin{corollary}
Every integer dilation of a lattice $3$-polytope of width $1$ has a unimodular cover.
\end{corollary}

We believe that the $3$-polytopes in all these statements all have unimodular triangulations, but this remains an open question.

\subsection*{Acknowledgements:} We thank Akiyoshi Tsuchiya, Spencer Backman, and Johannes Hofscheier for posing these questions to us and 
Christian Haase for helpful discussions.

@@

Consider the segment $s$ contained in $r_1' + \vecline p$ with endpoints $s_1=r_1'$ on $d$ and $s_2$ on $d'$.  
Since $t$ separates $q_1$ and $q_1+q_2-p_1$ and $g$ decreases from $t_1$ to $t_2$ (by \Cref{claim:g}), the inequality $g(x)< g(d')$ holds on $Q\cap V_2$,
and in particular for $r_2'$. Since $r_2'$ is a lattice point, $g(r_2')\leq g(d)= g(r_1')$, which contradicts \Cref{claim:g}).
\end{proof}
\giulia{add a picture!}
